---
title: "Making plots to explore data using R"
subtitle: "Using wages data in the yowie package"
author: 
  - "<br><br>Di Cook, Monash University"
date: 'NYC R Ladies - Aug 24/25, 2021 <br> Slides: [https://dicook.org/files/NYC_RLadies/slides.html](https://dicook.org/files/NYC_RLadies/slides.html) <br> [https://github.com/dicook/NYC_RLadies/](https://github.com/dicook/NYC_RLadies/)'
output:
  xaringan::moon_reader:
    css: ["mystyle.css", xaringan-themer.css]
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#035AA6", 
  secondary_color = "#03A696", 
  background_color = "#002B36", # dark dark blue
  header_color = "#31b09e",     # light aqua green
  link_color = "#31b09e",
  code_inline_color = "#31b09e",
  code_font_size = "1em",
  text_color = "#FFF",
  text_font_google = google_font("Schoolbell"),
  header_font_google = google_font("Sunshiney"),
  text_font_size = "2em", 
  title_slide_background_image = "images/yowie.png",
  title_slide_background_size = "15%",
  title_slide_background_position = "99% 1%"
)
slides_from_images <- function(
  path,
  regexp = NULL,
  class = "hide-count",
  background_size = "contain",
  background_position = "top left"
) {
  if (isTRUE(getOption("slide_image_placeholder", FALSE))) {
    return(glue::glue("Slides to be generated from [{path}]({path})"))
  }
  if (fs::is_dir(path)) {
    imgs <- fs::dir_ls(path, regexp = regexp, type = "file", recurse = FALSE)
  } else if (all(fs::is_file(path) && fs::file_exists(path))) {
    imgs <- path
  } else {
    stop("path must be a directory or a vector of images")
  }
  imgs <- fs::path_rel(imgs, ".")
  breaks <- rep("\n---\n", length(imgs))
  breaks[length(breaks)] <- ""

  txt <- glue::glue("
  class: {class}
  background-image: url('{imgs}')
  background-size: {background_size}
  background-position: {background_position}
  {breaks}
  ")

  paste(txt, sep = "", collapse = "")
}
```

## About me

Hi!
I'm Di, which rhymes with .red[t].orange[i].yellow[e]-.green[d].blue[y].purple[e]
--

<br>I'm a professor at Monash University in Melbourne, Australia
--

<br>I've been working with R for a long time, and with S before that. It's hard to keep up with the changes. 
--

<br><br> If you feel comfortable, say hello in the chat and tell me about yourself

---
# Motivation

Hullman and Gelman (2021) [Designing for Interactive Exploratory Data Analysis Requires Theories of Graphical Inference](https://hdsr.mitpress.mit.edu/pub/w075glo6/release/2)

- Interplay between exploratory data analysis (EDA) and confirmatory data analysis (CDA)
- Concerns about lack of tools for testing findings in exploratory data analysis, particularly using graphics

# What is EDA, IDA, MD, InfoVis?

---
background-color: #FFF

`r slides_from_images("images/EDA-CDA")`

---
# Longitudinal study of wages in the USA

Data is available in the `yowie` package. You can install it using; 

```
remotes::install_github("numbats/yowie")
```

`yowie`: .aqua[Y]ears .aqua[O]f .aqua[W]ages to .aqua[I]nvestigate and .aqua[E]xplore 

> Let's get started by opening the `wages.R` file in RStudio 

---
class: center, middle

# Thanks!

Slides created via the R packages:

[**xaringan**](https://github.com/yihui/xaringan)<br>
[gadenbuie/xaringanthemer](https://github.com/gadenbuie/xaringanthemer)

The chakra comes from [remark.js](https://remarkjs.com), [**knitr**](http://yihui.name/knitr), and [R Markdown](https://rmarkdown.rstudio.com).
